Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-06 Thesis/04-chap4.qmd
make latex happy by removing checker message

```{r}
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
                   keras_model = get_keras_model("vss_phn_32"))
checker$check()
```

```{r message=TRUE}
checker
```

```{r}
checker$summary_plot()
```

@@

```{r echo=TRUE, message=TRUE}
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
                   keras_model = get_keras_model("vss_phn_32"))
checker
```

@@

For a visual test conducted by a single observer using the lineup protocol, the minimum $p$-value is $1/m$, where $m$ is the number of residual plots in a lineup. This is because the Type-I error of this test is $1/m$. Similarly, when performing a lineup check via the `lineup_check` method, the checker generates $m−1$ null plots to combine with the true residual plot, forming a lineup. It then calculates the $p$-value as the ratio of plots with visual signal strength greater than or equal to that of the true plot. The $p$-value of this test is also bounded by $1/m$.

@@

```{r echo=TRUE, message=TRUE}
checker
```

>>>>

```{r}
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
                   keras_model = get_keras_model("vss_phn_32"))
checker$plot_resid()
```

```{r}
checker$check()
```

```{r}
checker
```

```{r echo=TRUE}
checker$summary_plot()
```

@@

```{r echo=TRUE}
library(autovi)
checker <- auto_vi(fitted_model = lm(dist ~ speed, data = cars), 
                   keras_model = get_keras_model("vss_phn_32"))
checker
```

@@

For a visual test conducted by a single observer using the lineup protocol, the minimum $p$-value is $1/m$, where $m$ is the number of residual plots in a lineup. This is because the Type-I error of this test is $1/m$. Similarly, when performing a lineup check via the `lineup_check` method, the checker generates $m-1$ null plots to combine with the true residual plot, forming a lineup. It then calculates the $p$-value as the ratio of plots with visual signal strength greater than or equal to that of the true plot. The $p$-value of this test is also bounded by $1/m$.

@@

```{r echo=TRUE}
checker
```
